\chapter{Abstract}
\label{chap:abstract}

The world energy consumption has dramatically increased since the end
of the World War II. The main share of this energy comes from fossil
fuel combustion. The worldwide domestic sector consumes about 30\% of
the global energy supply and the biggest share of that is dedicated to
space and water heating. In this context where sustainable energy
consumption is required to limit our impact on the environment and the
climate, energy efficiency is a key factor to successfully transition
to energy sobriety. Electrically-driven heat pumps are known to be a
key technology to increase our energy efficiency. More efficient, more
compact, more silent heat pumps, built with less raw material, and
using lower refrigerant charges are needed. In electrically-driven
heat pumps, the compression phase is responsible for most of the
energy losses. However, for decades now, the heat pump performance has
been stagnating, mainly because of the compression phase efficiency
which has not been increasing significantly. Consequently, the
improvement of the compression phase is indeed needed. A new
single-stage compression unit design has been developed, built, and
tested in a previous thesis work. This thesis work uses a twin-stage
successor of the initial single-stage compression unit and tests it
into two oil-free domestic heat pump prototypes. This work aims at
studying the integration of the radial compression units in domestic
heat pumps and at demonstrating their feasibility and potential. The
tested prototypes are a twin-stage Air/Water domestic heat pump and a
twin-stage Brine/Water domestic heat pump. Both of them are equipped
with a twin-stage oil-free radial compression unit rotating on gas
bearings. By which, the maximum rotor speed of the compression units
is 180 krpm. Six stable operation points have been documented with the
Air/Water heat pump prototype. More notably so, the operating point
A-7/W35 has been reached and demonstrates a coefficient of performance
of 2.36 for a heating power of 10.7 kW. The Brine/Water heat pump
prototype has been used to perform partial tests of circuit
improvements, in order to solve some of the issues observed on the
Air/Water prototype. The analysis of the experimental results uses a
mass and energy balance modeling approach to improve the level of
understanding of the internal and non measurable flows in the heat
pump circuits. This model also propagates the uncertainties of the
measurements through the equations. New improvements and innovative
circuit layouts, notably at the level of the economizer, key-component
of the two-stage heat pump circuit, are offered to integrate further
the compression unit in the heat pump circuits, and to make the whole
system more efficient, compact, silent, less demanding in raw
materials and reducing the refrigerant charge needed for the heat pump
cycle.

\vspace{10mm}

Keywords:~\varuskeywords
