%%% Nomenclature %%%

%%% Romans

\nomenclature[A]{$P$}{Absolute pressure, pressure \nomunitwo{[\si{\pascal}]}}
\nomenclature[A]{$T$}{Temperature \nomunitwo{[\si{\kelvin}]}}
\nomenclature[A]{$h$}{Specific enthalpy \nomunitwo{[\si{\joule\per\kilo\gram}]}}
\nomenclature[A]{$s$}{Specific entropy \nomunitwo{[\si{\joule\per\kilo\gram\per\kelvin}]}}
\nomenclature[A]{$\dot{M}$}{Mass flow rate \nomunitwo{[\si{\kilo\gram\per\second}]}}

%%% Greeks

\nomenclature[B]{$\Pi$}{Pressure ratio
  \nomunit{$\left[-\right]$}{eq:PR}}
\nomenclature[B]{$\epsilon$}{Coefficient of Performance,
  effectiveness\index{effectiveness}
  \nomunit{$\left[-\right]$}{eq:COPh}}
\nomenclature[B]{$\mu$}{Uncertainty of the reference probe
  \nomunitwo{$\left[\text{K}\right]$}}
\nomenclature[B]{$\kappa$}{Angle of rotation
  \nomunitwo{$\left[\text{rad}\right]$}}
\nomenclature[B]{$\theta$}{Angle of rotation
  \nomunitwo{$\left[\text{rad}\right]$}}
\nomenclature[B]{$\Psi$}{Angle of rotation
  \nomunit{$\left[\text{rad}\right]$}{eq:psi}}
\nomenclature[B]{$\phi$}{Angle of rotation
  \nomunitwo{$\left[\text{rad}\right]$}}
\nomenclature[B]{$\eta$}{Exergy\index{exergy} efficiency\index{exergy
    efficiency}, efficiency
  \nomunit{$\left[-\right]$}{sec:methodo-indicators}}

%%% Subscripts

\nomenclature[C]{$out$}{outlet, output} \nomenclature[C]{$in$}{Inlet,
  input} \nomenclature[C]{$mot$}{motor\index{motor}}
\nomenclature[C]{$inv$}{inverter\index{inverter}}
\nomenclature[C]{$trans$}{transmission}
\nomenclature[C]{$tip$}{tip of the impeller}
\nomenclature[C]{$scaled$}{used if the value is scaled}
\nomenclature[C]{$rotated$}{used if the value is represented in a
  rotated axis system}
\nomenclature[C]{$sc$}{subcooling, subcooler\index{subcooler}}
\nomenclature[C]{$cp$}{compressor\index{compressor}}
\nomenclature[C]{$imp$}{impeller\index{impeller}}
\nomenclature[C]{$h$}{heating}
\nomenclature[C]{$s$}{isentropic (when follows the symbol $\eta$)}
\nomenclature[C]{$axi$}{axial}
\nomenclature[C]{$rad$}{radial}

%%% Non-dimensional numbers

% \nomenclature[D]{$Re$}{Reynolds number \nomunit{-}{eq:xx}}

%%% Glossary %%%

\storeglosentry{glos:economizer}{name={economizer},description={Also
    called flash tank, this is the second-stage liquid-vapor
    separator.},sort={economizer}}

\storeglosentry{glos:bold}{name={\textbf{bold value}},description={In a
    tabular only, this means that the value is measured. Consequently,
    its uncertainty is directly a result of the
    measurement.},sort={Z}}

\storeglosentry{glos:underline}{name={\underline{underlined
    value}},description={In a tabular only, this means that the value
    is guessed by the optimizer directly. Consequently, it does not benefit from the uncertainties propagation.},sort={Z}}

\storeglosentry{glos:normal-font}{name={value with normal
    font},description={In a tabular only, this means that the value
    is computed with the model, but it is not guessed directly. Consequently, it benefits from the uncertainties propagation.},sort={Z}}

%%% Acronyms %%%

\newacronym[ODP]{\textsc{ODP}}{Ozone Depletion
  Potential}{description={The ozone depletion potential (ODP) of a
    chemical compound is the relative amount of degradation to the
    ozone layer it can cause. R-11 ODP is the reference (ODP=1.0).}}

\newacronym[GWP]{\textsc{GWP}}{Global Warming Potential}{description={
    The global warming potential is a relative measure of how much
    heat energy a greenhouse gas traps in the atmosphere.}}

\newacronym[AWP]{\textsc{AWP}}{Air-Water twin-stage heat pump
  Prototype}{description={Air-Water twin-stage oil-free domestic heat
    pump powered by an oil-free twin-stage radial compression unit,
    rotating on gas bearings.}}

\newacronym[BWP]{\textsc{BWP}}{Brine-Water twin-stage heat pump
  Prototype}{description={Brine-Water twin-stage oil-free domestic heat
    pump powered by an oil-free twin-stage radial compression unit,
    rotating on gas bearings.}}

\newacronym[COP]{$\epsilon_h$}{heating effectiveness}{description={
    Ratio between heat power supplied to the hot source and the
    consumed work power, also called heating Coefficient Of
    Performance ($COP_h$), defined in \cref{sec:methodo-indicators}.}}

\newacronym[OP]{\textsc{OP}}{Operating Point}{description={An
    operating point is a specific point within the operation range of
    the heat pump cycle. It is characterized by two level of
    temperature: the cold source inlet temperature and the hot source
    outlet temperature. The operation point is named with those two
    temperatures preceded by the first letter of the source. The first
    part of the name concerns the cold source and the second part
    concerns the hot source. A slash separates the two parts. The
    letter \textit{A} stands for air, the letter \textit{B} stands for
    brine, and the letter \textit{W} stands water.}}


\newacronym[REFPROP]{REFPROP}{NIST Reference Fluid Thermodynamic and
  Transport Properties Database}{description={Program using equations
    for the thermodynamic and transport properties to calculate the
    state points of fluids or mixtures.}}
